\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-05 analysis/paper/paper.Rmd
working on species classification result table

We trained a random forest (RF) classifier to predict species based on NEON hyperspectral reflectance data.
RF is a machine learning approach that utilizes an ensemble of decision trees and iterative subsets of the training data.
We performed hyperparameter optimization of ntree, the number of decision trees in the forest, and mtry, the number of variables randomly sampled at each node in the tree.
We used the optimal values of 27 for mtry and 1000 for ntree in our final RF model.
We computed overall accuracy, confusion matrices, and variable importance plots.

@@

>>>>

We trained a random forest (RF) classifier to predict species based on NEON hyperspectral reflectance data.
RF is a machine learning approach that utilizes an ensemble of decision trees and iterative subsets of the training data.
We performed hyperparameter optimization of ntree, the number of decision trees in the forest, and mtry, the number of variables randomly sampled at each node in the tree.
We used the optimal values of 27 for mtry and 1000 for ntree in our final RF model.
There were 49 species classes and 
We computed overall accuracy, confusion matrices, and variable importance plots.

@@

We report overall classification accuracy of the species and genus classification:

df <- data.frame(oa = c("species", "genus", 382, 384),
                 species = c(94, 1220, 1733, 2922),
                 genus = )
